Create year end summaries

### 2023-07-24 src/year-end-summary.Rmd
Updated year-end-summary

update <- FALSE
print("Check 1")
```

@@

# Check source
check_source <- function(file_text) {
  message <- NULL
  file_text %>%
    str_subset("^source\\: ") %>%
    str_remove(fixed("source: ")) %>%
    str_remove_all('"')  %>%
    str_remove_all("'") -> file_source
  if (length(file_source)==0) {
    message <- glue("{yy}/{fn} has no source\n")
  }
  if (length(file_source)>1) {
    message <- glue("{yy}/{fn} has multiple sources\n")
  }
  return(message)
}

# Check date
check_date <- function(file_text) {
  message <- NULL
  file_text %>%
    str_subset("^date\\: ") %>%
    str_remove(fixed("date: ")) %>%
    str_remove_all('"') %>%
    str_remove_all("'")  -> message
  if (length(message)==0) {message <- glue("{yy}/{fn} has no date")}
  if (length(message)>1) {message <- glue("{yy}/{fn} has multiple dates")}
  return(message)
}

# Check title

# Create links for each file
create_file_list <- function(f, date_list) {
  f %>%
    str_replace(fixed(".Rmd"), "") %>%
    str_replace(fixed(".md"), "") -> short_name
  o <- order(date_list, f)
  glue("+ {date_list[o]} [{short_name[o]}](http://new.pmean.com/{short_name[o]}/)  ") %>%
    paste(collapse="  \n")
}
```

>>>>

update <- TRUE
print("Check 1")
```

@@

# Check source
check_source <- function(file_text) {
  message <- NULL
  file_text %>%
    str_subset("^source\\: ") %>%
    str_remove(fixed("source: ")) %>%
    str_remove_all('"')  %>%
    str_remove_all("'") -> file_source
  if (length(file_source)==0) {
    message <- glue("{yy}/{fn} has no source\n")
  }
  if (length(file_source)>1) {
    message <- glue("{yy}/{fn} has multiple sources\n")
  }
  return(message)
}
```

```{r}
# Check date
check_date <- function(file_text) {
  message <- NULL
  file_text %>%
    str_subset("^date\\: ") %>%
    str_remove(fixed("date: ")) %>%
    str_remove_all('"') %>%
    str_remove_all("'")  -> message
  if (length(message)==0) {message <- glue("{yy}/{fn} has no date")}
  if (length(message)>1) {message <- glue("{yy}/{fn} has multiple dates")}
  return(message)
}

# Check title
```

```{r}
# Create links for each file
create_file_list <- function(f, date_list) {
  f %>%
    str_replace(fixed(".Rmd"), "") %>%
    str_replace(fixed(".md"), "") -> short_name
  o <- order(date_list, f)
  glue("+ {date_list[o]} [{short_name[o]}](http://new.pmean.com/{short_name[o]}/)  ") %>%
    paste(collapse="  \n")
}
```
